\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-18 doc/paper.Rmd
starting points defined

\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\gk}[1]{{\textcolor{green}{#1}}}
\newcommand{\cited}[1]{{\textcolor{red}{#1}}}

@@

More precisely, \citet{hadler} define same-shift pairs of length $w_v$ to start in $(q^{(1)}_i, q^{(2)}_i)$, where $q^{(k)}_i$ has the form
\begin{eqnarray*}
q^{(k)}_i &=& t_k^* + i w_v \text{ for } i = -1, -2, ...\\
q^{(k)}_i &=& t_k^* + w_ o + i w_v \text{ for } i = 0, 1, 2, ...
\end{eqnarray*}
for all integer values of $i$ for which both $0 <  q^{(1)}_i \le T_1 - w_v$ and $0 <  q^{(2)}_i \le T_2 - w_v$.

Similarly, different-shift pairs are based on signature segments of length $w_v$ starting in $(q^{(1)}_i, q^{(2)}_{-i})$, for all integer values of $i$ for which both $0 <  q^{(1)}_i \le T_1 - w_v$ and $0 <  q^{(2)}_{-i} \le T_2 - w_v$.

@@

For both samples the correlations between the pairs of markings is then calculated. 
The intuition here is that for two markings from the same source the correlation for the in-phase sample should be high, while the correlations of the out-of-phase sample  provide a measure for the base-level correlation for non-matching marks of a given length $w_v$. The Chumbley score is then computed as a Mann Whitney U statistic to compare between in-phase sample and out-of-phase sample. 
In the original method proposed in \citet{chumbley} both in-phase and out-of-phase sample are extracted randomly, whereas \citet{hadler} proposed deterministic rules for both samples to make the resulting score deterministic while simultaneously avoiding overlaps within selected marks to ensure independence.

>>>>

\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\gk}[1]{{\textcolor{green}{#1}}}
\newcommand{\cited}[1]{{\textcolor{red}{#1}}}
\setlength\parindent{0pt}

@@

More precisely, let us define starting points $s_i^{(k)}$ for each signature $k = 1, 2$ as 
\begin{eqnarray*}
s^{(k)}_i = 
\begin{cases}
t_k^* + i w_v & \text{ for } i < 0 \\
t_k^* + w_ o + i w_v & \text{ for } i \ge 0,
\end{cases}
\end{eqnarray*} for integer values of $i$ with $0 <  s^{(k)}_i \le T_k - w_v$.

Same-shift pairs of length $w_v$ are defined in \citet{hadler} as all 
pairs $(s_i^{(1)}, s_i^{(2)})$ for all integer values $i$ for which both $s_i^{(1)}$ and  $s_i^{(2)}$ are defined. Similarly, different-shift pairs are defined as $(s_i^{(1)}, s_{-i}^{(2)})$ for all $i$ where both $s_i^{(1)}$ and  $s_{-i}^{(2)}$ are defined.

@@

For both same- and different-shift pairs correlations between the  markings are calculated. 
The intuition here is that for two markings from the same source the correlation for the in-phase sample should be high, while the correlations of the out-of-phase sample  provide a measure for the base-level correlation for non-matching marks of a given length $w_v$. The Chumbley score is then computed as a Mann Whitney U statistic to compare between in-phase sample and out-of-phase sample. 
In the original method proposed in \citet{chumbley} both in-phase and out-of-phase sample are extracted randomly, whereas \citet{hadler} proposed the above specified deterministic rules for both samples to make the resulting score deterministic while simultaneously avoiding overlaps within selected marks to ensure independence.

### 2018-04-18 doc/paper.tex
starting points defined

@@

More precisely, \citet{hadler} define same-shift pairs of length \(w_v\)
to start in \((q^{(1)}_i, q^{(2)}_i)\), where \(q^{(k)}_i\) has the form

\begin{eqnarray*}
q^{(k)}_i &=& t_k^* + i w_v \text{ for } i = -1, -2, ...\\
q^{(k)}_i &=& t_k^* + w_ o + i w_v \text{ for } i = 0, 1, 2, ...
\end{eqnarray*}

for all integer values of \(i\) for which both
\(0 < q^{(1)}_i \le T_1 - w_v\) and \(0 < q^{(2)}_i \le T_2 - w_v\).

Similarly, different-shift pairs are based on signature segments of
length \(w_v\) starting in \((q^{(1)}_i, q^{(2)}_{-i})\), for all
integer values of \(i\) for which both \(0 < q^{(1)}_i \le T_1 - w_v\)
and \(0 < q^{(2)}_{-i} \le T_2 - w_v\).

@@

For both samples the correlations between the pairs of markings is then
calculated. The intuition here is that for two markings from the same
source the correlation for the in-phase sample should be high, while the
correlations of the out-of-phase sample provide a measure for the
base-level correlation for non-matching marks of a given length \(w_v\).
The Chumbley score is then computed as a Mann Whitney U statistic to
compare between in-phase sample and out-of-phase sample. In the original
method proposed in \citet{chumbley} both in-phase and out-of-phase
sample are extracted randomly, whereas \citet{hadler} proposed
deterministic rules for both samples to make the resulting score
deterministic while simultaneously avoiding overlaps within selected
marks to ensure independence.

>>>>

\setlength\parindent{0pt}

@@

More precisely, let us define starting points \(s_i^{(k)}\) for each
signature \(k = 1, 2\) as

\begin{eqnarray*}
s^{(k)}_i = 
\begin{cases}
t_k^* + i w_v & \text{ for } i < 0 \\
t_k^* + w_ o + i w_v & \text{ for } i \ge 0,
\end{cases}
\end{eqnarray*}

for integer values of \(i\) with \(0 < s^{(k)}_i \le T_k - w_v\).

Same-shift pairs of length \(w_v\) are defined in \citet{hadler} as all
pairs \((s_i^{(1)}, s_i^{(2)})\) for all integer values \(i\) for which
both \(s_i^{(1)}\) and \(s_i^{(2)}\) are defined. Similarly,
different-shift pairs are defined as \((s_i^{(1)}, s_{-i}^{(2)})\) for
all \(i\) where both \(s_i^{(1)}\) and \(s_{-i}^{(2)}\) are defined.

@@

For both samples the correlations between the pairs of markings are then
calculated. The intuition here is that for two markings from the same
source the correlation for the in-phase sample should be high, while the
correlations of the out-of-phase sample provide a measure for the
base-level correlation for non-matching marks of a given length \(w_v\).
The Chumbley score is then computed as a Mann Whitney U statistic to
compare between in-phase sample and out-of-phase sample. In the original
method proposed in \citet{chumbley} both in-phase and out-of-phase
sample are extracted randomly, whereas \citet{hadler} proposed
deterministic rules for both samples to make the resulting score
deterministic while simultaneously avoiding overlaps within selected
marks to ensure independence.
